
#### 1 - Descriptive Stats and Visuals 
In this part, I will assemble the main functions and methods used to generate summary statistics.
I will also try to join these summary statistics functions with all the visual graphs that make exploring any data set easy and fun.

```{r  results=FALSE, include=TRUE, warning=FALSE,message=FALSE}
########################################################################
#            Loading Libraries
########################################################################

library(caTools)
library(gridExtra)
library(Hmisc) ## for the "describe" function
library(pastecs) ## for the "stat.desc" function
library(scales)  #3 for the "percent_scales" function

```


## Loading the Titanic Data set:

This data is available and can be downloaded from Kaggle
https://www.kaggle.com/c/titanic/data

```{r}
# We load the train and test libraries
train<-read.csv(file.choose())
# test<-read.csv(file.choose())

# to make it easy to build some graphs, we change the type of the variable Survived (values = 1 and = 0)
train$Survived<-as.factor(train$Survived)
head(train)
summary(train)
describe(train)
stat.desc(train)
```
#### Building Some Graphs 

```{r}
### ploting some graphs
## We use the ggplot2 Library

#ploting survivors per passer class

g1 <- ggplot(train, aes(Pclass))
g1 + geom_bar(stat = "count",aes(fill = Survived))+
    ggtitle("Survivors By Passenger Class") 
## Survivors by Gender
g2 <- ggplot(train, aes(Sex))
g2 + geom_bar(stat = "count",aes(fill = Survived))+
    ggtitle("Survivors By Passenger Gender")

##Survivors By Port of Embarkment
g3 <- ggplot(train, aes(Embarked))
g3 + geom_bar(stat="count",aes(fill = factor(Survived)))+
    scale_y_continuous(labels = percent_format())+
    ggtitle("Survivors By Port of Embarkment")

```


### comments to be added to each section


